Molecular Gas Kinematics and Star Formation Properties of the Strongly-Lensed Quasar Host Galaxy RXS J1131$-$1231

### 2016-12-13 WRITEUP/response.md

"Interpretation of CO, Radio, Optical, and IR Continuum 
observations of the Strongly Lensed Host Galaxy of the 
Quasar RXS J1131-1231"

or simply:

"CO, Radio, Optical, and IR results on 
the Lensed Host Galaxy of the Quasar RXS J1131-1231".

# RESPONSE:
1a) To take the referee's point into account, we have changed the title to "Molecular gas kinematics and star formation properties of the strongly lensed quasar host galaxy RXSJ1131-1231". We agree that we study more than just the CO gas of the science target in this paper; however, a large fraction of the paper is based on our new CO data and the analysis (including lens modeling) on which we thus place an emphasis.

@@

So you need not quote these fluxes to three decimal places.

Because of these flux errors, you also cannot quote the spectral
index of the foreground galaxy to three decimal places
(Sect. 3.3, last sentence).

# RESPONSE:
It is the standard practice to report flux measurement uncertainties from interferometric observations separate from those due to absolute flux calibration and state those in the observations section (i.e. Section 2). However, we note that uncertainties from absolute flux calibration are taken into account when deriving the error bars associated with physical parameters throughout the paper. To address the referee's concern, we have added remarks in Table 1, and Section 4.5 paragraph 1 to remind the reader of these uncertainties.

We have updated the number of decimals in the spectral indices reported in Section 3.3, as suggested by the referee.

### 2016-12-13 WRITEUP/diff.tex
update tone

\begin{abstract}
We report observations of \bco and \cco line emission towards
the quadruply-lensed quasar
RXS\,J1131$-$1231 at $z$\,=\,0.654 obtained using the
\pdbi (PdBI) and the \carma (CARMA).
Our lens modeling shows that the asymmetry in the double-horned \bco line profile
is mainly a result of differential lensing, where
the magnification factor varies from $\sim$3 to $\sim$9 across
different kinematic components.
The intrinsically symmetric line profile with a conspicuous source-plane velocity
gradient suggests that
the host galaxy is an extended rotating disk, with a CO size of $R_{\rm CO}$$\sim$6\,kpc and
a dynamical mass of $M_{\rm dyn}$\ssim8\E{10}\,\Msun.
In addition, we find a secondary CO-emitting source near RXS\,J1131$-$1231 whose location is
consistent with the optically-faint companion reported in previous studies.
The lensing-corrected molecular gas masses are $M_{\rm gas}$\eq(1.4\pmm0.3)\E{10}\,\Msun
and (2.0\pmm0.1)\E{9}\,\Msun for RXS\,J1131$-$1231 and the companion, respectively.
The gas mass fraction of \old{$\sim$19\% } \new{$\sim$18\pmm4\%} is consistent with the trend of decreasing molecular gas fraction since $z$\ssim2 reported in recent studies.
\old{We find lensing-corrected stellar and dust masses, an IR luminosity, and a
star formation rate of
\mbox{$M_{*}$\eq(3\pmm1)\E{10}\,\Msun}, \mbox{$M_{\rm dust}$\ssim3\E{8}\,\Msun}, \mbox{$L_{\rm IR}$\ssim1.5\E{12}\,\Lsun}, and \mbox{SFR$_{\rm FIR}$\eq(120\pmm63)\,\sfrU} for RXS\,J1131$-$1231.
The source-plane morphologies of its gas and stellar populations
indicate that the star-formation activity may be as extended as the molecular gas reservoir.
We find a \mbox{$M_{\rm BH}$$/$$M_{\rm bulge}$} ratio of \mbox{$>$0.27\petm{0.11}{0.08}\%} which is higher
than the
local value, suggesting that the bulk of the black hole mass of RXSJ1131-1231 is largely in place while its stellar bulge is still assembling.}
\new{We find a lensing-corrected stellar mass of
$M_{*}$\eq(3\pmm1)\E{10}\,\Msun and a star formation rate of SFR$_{\rm FIR}$\eq(120\pmm63)\,\sfrU,
corresponding to a specific SFR and star formation efficiency that are comparable to non-quasar host 
disk galaxies at $z$\ssim1.
This together with a gas mass fraction following the redshift evolution indicates
that no evidence for quenching of star formation is seen in RXS\,J1131$-$1231.
This is in agreement with the elevated \mbox{$M_{\rm BH}$$/$$M_{\rm bulge}$} ratio of \mbox{$>$0.27\petm{0.11}{0.08}\%} compared to the
local value, suggesting that the bulk of the black hole 
mass of RXSJ1131-1231 is largely in place while its stellar bulge is still assembling.}
\end{abstract}

@@

The specific star formation rate (sSFR\eq SFR/$M_*$) of 4\petm{2.6}{2.4}\,Gyr\pmOne derived for RXJ1131
is $\lesssim$1.5$\sigma$ above the main sequence according to
the redshift-dependent ``main sequence'' relation in \citet[and references therein]{Tacconi13a}.
Given that RXJ1131 share similar \SF rate, \SF efficiency, and CO disk size as other ``main sequence'' disk galaxies,
the small elevation in sSFR over the main sequence at $z$\ssim0.7 suggests
that the \SF activity in RXJ1131 may be enhanced by interactions with the companion.
\new{In addition, a SFE and sSFR comparable to those of high-$z$ disk 
galaxies, which are not known to host AGNs,
together with a molecular gas mass fraction that follows the redshift evolution reported in other studies (\Sec{frac})
suggest that no quenching of star formation is observed in RXJ1131, despite 
that fact that it is hosting a quasar.
Hence, the decline in star formation history since $z$\ssim2 
for at least a subset of AGN host galaxies 
may be mainly
a manifestation of the evolution in the molecular gas content rather than a result of 
the negative feedback driven by their central AGNs.
}

@@

\new{Theoretical studies have suggested that negative feedback from an AGN may remove a 
large fraction of the molecular gas from its host galaxy, thereby quenching its star formation \mbox{\citep[e.g., ][]{DiMatteo05a}}.
In this study, we find that the star formation efficiency and specific SFR derived for RXJ1131 are comparable to those of 
non-AGN host disk galaxies at $z$\ssim1$-$1.5, and that the 
derived molecular gas mass fraction is consistent with the redshift evolution reported in other studies. 
We thus find no evidence of negative AGN feedback on the molecular gas content 
and on the star formation activity in RXJ1131 at the resolution of our data.
Our results may be hinting that at least for a subset of AGN host galaxies at intermediate redshift,
their contribution to the decline in cosmic star formation history since $z$\ssim2 
may be mainly
a manifestation of the redshift evolution in the molecular gas content rather than a result of 
negative feedback driven by their central AGNs.
}

>>>>

\begin{abstract}
We report observations of \bco and \cco line emission towards
the quadruply-lensed quasar
RXS\,J1131$-$1231 at $z$\,=\,0.654 obtained using the
\pdbi (PdBI) and the \carma (CARMA).
Our lens modeling shows that the asymmetry in the double-horned \bco line profile
is mainly a result of differential lensing, where
the magnification factor varies from $\sim$3 to $\sim$9 across
different kinematic components.
The intrinsically symmetric line profile with a conspicuous source-plane velocity
gradient suggests that
the host galaxy is an extended rotating disk, with a CO size of $R_{\rm CO}$$\sim$6\,kpc and
a dynamical mass of $M_{\rm dyn}$\ssim8\E{10}\,\Msun.
In addition, we find a secondary CO-emitting source near RXS\,J1131$-$1231 whose location is
consistent with the optically-faint companion reported in previous studies.
The lensing-corrected molecular gas masses are $M_{\rm gas}$\eq(1.4\pmm0.3)\E{10}\,\Msun
and (2.0\pmm0.1)\E{9}\,\Msun for RXS\,J1131$-$1231 and the companion, respectively.
The gas mass fraction of \old{$\sim$19\% } \new{$\sim$18\pmm4\%} is consistent with the trend of decreasing molecular gas fraction since $z$\ssim2 reported in recent studies.
\old{We find lensing-corrected stellar and dust masses, an IR luminosity, and a
star formation rate of
\mbox{$M_{*}$\eq(3\pmm1)\E{10}\,\Msun}, \mbox{$M_{\rm dust}$\ssim3\E{8}\,\Msun}, \mbox{$L_{\rm IR}$\ssim1.5\E{12}\,\Lsun}, and \mbox{SFR$_{\rm FIR}$\eq(120\pmm63)\,\sfrU} for RXS\,J1131$-$1231.
The source-plane morphologies of its gas and stellar populations
indicate that the star-formation activity may be as extended as the molecular gas reservoir.
We find a \mbox{$M_{\rm BH}$$/$$M_{\rm bulge}$} ratio of \mbox{$>$0.27\petm{0.11}{0.08}\%} which is higher
than the
local value, suggesting that the bulk of the black hole mass of RXSJ1131-1231 is largely in place while its stellar bulge is still assembling.}
\new{We find a lensing-corrected stellar mass of
$M_{*}$\eq(3\pmm1)\E{10}\,\Msun and a star formation rate of SFR$_{\rm FIR}$\eq(120\pmm63)\,\sfrU,
corresponding to a specific SFR and star formation efficiency that are comparable to non-quasar host 
disk galaxies at $z$\ssim1.
This together with a gas mass fraction following the redshift evolution indicates
that no evidence for quenching of star formation is seen in RXS\,J1131$-$1231.
This is in agreement with its elevated \mbox{$M_{\rm BH}$$/$$M_{\rm bulge}$} ratio of \mbox{$>$0.27\petm{0.11}{0.08}\%} compared to the
local value, suggesting that the bulk of its black hole 
mass is largely in place while its stellar bulge is still assembling.}
\end{abstract}

@@

The specific star formation rate (sSFR\eq SFR/$M_*$) of 4\petm{2.6}{2.4}\,Gyr\pmOne derived for RXJ1131
is $\lesssim$1.5$\sigma$ above the main sequence according to
the redshift-dependent ``main sequence'' relation in \citet[and references therein]{Tacconi13a}.
Given that RXJ1131 share similar \SF rate, \SF efficiency, and CO disk size as other ``main sequence'' disk galaxies,
the small elevation in sSFR over the main sequence at $z$\ssim0.7 suggests
that the \SF activity in RXJ1131 may be enhanced by interactions with the companion.
\new{In addition, a SFE and sSFR comparable to those of high-$z$ disk 
galaxies, which are not known to host AGNs,
together with a molecular gas mass fraction that follows the redshift evolution reported in other studies (\Sec{frac})
suggest that no quenching of star formation is observed in RXJ1131, despite 
that fact that it is hosting a quasar.
This is suggestive that for some AGN host galaxies at intermediate redshift, 
their contribution to the decline in the cosmic star formation history since $z$\ssim2 is mainly a 
manifestation of the redshift evolution in the molecular gas content 
rather than a result of the negative feedback driven by their central AGNs.
}

@@

\new{Theoretical studies have suggested that negative feedback from an AGN may remove a 
large fraction of the molecular gas from its host galaxy, thereby quenching its star formation \mbox{\citep[e.g., ][]{DiMatteo05a}}.
In this study, we find that the star formation efficiency and specific SFR derived for RXJ1131 are comparable to those of 
non-AGN host disk galaxies at $z$\ssim1$-$1.5, and that the 
derived molecular gas mass fraction is consistent with the redshift evolution reported in other studies. 
We thus find no evidence of negative AGN feedback on the molecular gas content 
and on the star formation activity in RXJ1131 at the resolution of our data.
Our results suggest that for some AGN host galaxies at intermediate redshift, 
their contribution to the decline in the cosmic star formation history since $z$\ssim2 is mainly a 
manifestation of the redshift evolution in the molecular gas content 
rather than a result of the negative feedback driven by their central AGNs.
}

### 2016-12-13 WRITEUP/ms.tex
update tone

\begin{abstract}
We report observations of \bco and \cco line emission towards
the quadruply-lensed quasar
RXS\,J1131$-$1231 at $z$\,=\,0.654 obtained using the
\pdbi (PdBI) and the \carma (CARMA).
Our lens modeling shows that the asymmetry in the double-horned \bco line profile
is mainly a result of differential lensing, where
the magnification factor varies from $\sim$3 to $\sim$9 across
different kinematic components.
The intrinsically symmetric line profile with a conspicuous source-plane velocity
gradient suggests that
the host galaxy is an extended rotating disk, with a CO size of $R_{\rm CO}$$\sim$6\,kpc and
a dynamical mass of $M_{\rm dyn}$\ssim8\E{10}\,\Msun.
In addition, we find a secondary CO-emitting source near RXS\,J1131$-$1231 whose location is
consistent with the optically-faint companion reported in previous studies.
The lensing-corrected molecular gas masses are $M_{\rm gas}$\eq(1.4\pmm0.3)\E{10}\,\Msun
and (2.0\pmm0.1)\E{9}\,\Msun for RXS\,J1131$-$1231 and the companion, respectively.
The gas mass fraction of $f_{\rm gas}$\eq18\pmm4\% inferred for RXS\,J1131$-$1231 is consistent with the trend of decreasing molecular gas fraction since $z$\ssim2 reported in recent studies.
We find a lensing-corrected stellar mass of
$M_{*}$\eq(3\pmm1)\E{10}\,\Msun and a star formation rate of SFR$_{\rm FIR}$\eq(120\pmm63)\,\sfrU,
corresponding to a specific SFR and star formation efficiency that are comparable to non-quasar host 
disk galaxies at $z$\ssim1.
This together with a gas mass fraction following the redshift evolution indicates
that no evidence for quenching of star formation is seen in RXS\,J1131$-$1231.
This is in agreement with the elevated \mbox{$M_{\rm BH}$$/$$M_{\rm bulge}$} ratio of \mbox{$>$0.27\petm{0.11}{0.08}\%} compared to the
local value, suggesting that the bulk of the black hole 
mass of RXSJ1131-1231 is largely in place while its stellar bulge is still assembling.
\end{abstract}

@@

%
% %Tacconi13a: the best-fit MS, SFR would be 12.1 Msun/yr for MS given Mstar = 3e10.
% %sSFR (Gyr^-1) = 0.68 (Mstar/6.6e10)^-0.35((1+z)/2.2)^2.8 = 0.40 if RXJ on MS
The specific star formation rate (sSFR\eq SFR/$M_*$) of 4\petm{2.6}{2.4}\,Gyr\pmOne derived for RXJ1131
is $\lesssim$1.5$\sigma$ above the main sequence according to
the redshift-dependent ``main sequence'' relation in \citet[and references therein]{Tacconi13a}.
%  and is consistent with those of the \cite{dacunha10a} sample of local ULIRGs.
Given that RXJ1131 share similar \SF rate, \SF efficiency, and CO disk size as other ``main sequence'' disk galaxies,
the small elevation in sSFR over the main sequence at $z$\ssim0.7 suggests
that the \SF activity in RXJ1131 may be enhanced by interactions with the companion.
In addition, a SFE and sSFR comparable to those of high-$z$ disk 
galaxies, which are not known to host AGNs,
together with a molecular gas mass fraction that follows the redshift evolution reported in other studies (\Sec{frac})
suggest that no quenching of star formation is observed in RXJ1131, despite 
that fact that it is hosting a quasar.
Hence, the decline in star formation history since $z$\ssim2 
for at least a subset of AGN host galaxies 
may be mainly
a manifestation of the evolution in the molecular gas content rather than a result of 
the negative feedback driven by their central AGNs.

@@

Theoretical studies have suggested that negative feedback from an AGN may remove a 
large fraction of the molecular gas from its host galaxy, thereby quenching its star formation \mbox{\citep[e.g., ][]{DiMatteo05a}}.
In this study, we find that the star formation efficiency and specific SFR derived for RXJ1131 are comparable to those of 
non-AGN host disk galaxies at $z$\ssim1$-$1.5, and that the 
derived molecular gas mass fraction is consistent with the redshift evolution reported in other studies. 
We thus find no evidence of negative AGN feedback on the molecular gas content 
and on the star formation activity in RXJ1131 at the resolution of our data.
Our results may be hinting that at least for a subset of AGN host galaxies at intermediate redshift,
their contribution to the decline in cosmic star formation history since $z$\ssim2 
may be mainly
a manifestation of the redshift evolution in the molecular gas content rather than a result of 
negative feedback driven by their central AGNs.

>>>>

\begin{abstract}
We report observations of \bco and \cco line emission towards
the quadruply-lensed quasar
RXS\,J1131$-$1231 at $z$\,=\,0.654 obtained using the
\pdbi (PdBI) and the \carma (CARMA).
Our lens modeling shows that the asymmetry in the double-horned \bco line profile
is mainly a result of differential lensing, where
the magnification factor varies from $\sim$3 to $\sim$9 across
different kinematic components.
The intrinsically symmetric line profile with a conspicuous source-plane velocity
gradient suggests that
the host galaxy is an extended rotating disk, with a CO size of $R_{\rm CO}$$\sim$6\,kpc and
a dynamical mass of $M_{\rm dyn}$\ssim8\E{10}\,\Msun.
In addition, we find a secondary CO-emitting source near RXS\,J1131$-$1231 whose location is
consistent with the optically-faint companion reported in previous studies.
The lensing-corrected molecular gas masses are $M_{\rm gas}$\eq(1.4\pmm0.3)\E{10}\,\Msun
and (2.0\pmm0.1)\E{9}\,\Msun for RXS\,J1131$-$1231 and the companion, respectively.
The gas mass fraction of $f_{\rm gas}$\eq18\pmm4\% inferred for RXS\,J1131$-$1231 is consistent with the trend of decreasing molecular gas fraction since $z$\ssim2 reported in recent studies.
We find a lensing-corrected stellar mass of
$M_{*}$\eq(3\pmm1)\E{10}\,\Msun and a star formation rate of SFR$_{\rm FIR}$\eq(120\pmm63)\,\sfrU,
corresponding to a specific SFR and star formation efficiency that are comparable to non-quasar host 
disk galaxies at $z$\ssim1.
This together with a gas mass fraction following the redshift evolution indicates
that no evidence for quenching of star formation is seen in RXS\,J1131$-$1231.
This is in agreement with its elevated \mbox{$M_{\rm BH}$$/$$M_{\rm bulge}$} ratio of \mbox{$>$0.27\petm{0.11}{0.08}\%} compared to the
local value, suggesting that the bulk of its black hole 
mass is largely in place while its stellar bulge is still assembling.
\end{abstract}

@@

%
% %Tacconi13a: the best-fit MS, SFR would be 12.1 Msun/yr for MS given Mstar = 3e10.
% %sSFR (Gyr^-1) = 0.68 (Mstar/6.6e10)^-0.35((1+z)/2.2)^2.8 = 0.40 if RXJ on MS
The specific star formation rate (sSFR\eq SFR/$M_*$) of 4\petm{2.6}{2.4}\,Gyr\pmOne derived for RXJ1131
is $\lesssim$1.5$\sigma$ above the main sequence according to
the redshift-dependent ``main sequence'' relation in \citet[and references therein]{Tacconi13a}.
%  and is consistent with those of the \cite{dacunha10a} sample of local ULIRGs.
Given that RXJ1131 share similar \SF rate, \SF efficiency, and CO disk size as other ``main sequence'' disk galaxies,
the small elevation in sSFR over the main sequence at $z$\ssim0.7 suggests
that the \SF activity in RXJ1131 may be enhanced by interactions with the companion.
In addition, a SFE and sSFR comparable to those of high-$z$ disk 
galaxies, which are not known to host AGNs,
together with a molecular gas mass fraction that follows the redshift evolution reported in other studies (\Sec{frac})
suggest that no quenching of star formation is observed in RXJ1131, despite 
that fact that it is hosting a quasar.
This is suggestive that for some AGN host galaxies at intermediate redshift, 
their contribution to the decline in the cosmic star formation history since $z$\ssim2 is mainly a 
manifestation of the redshift evolution in the molecular gas content 
rather than a result of the negative feedback driven by their central AGNs.

@@

Theoretical studies have suggested that negative feedback from an AGN may remove a 
large fraction of the molecular gas from its host galaxy, thereby quenching its star formation \mbox{\citep[e.g., ][]{DiMatteo05a}}.
In this study, we find that the star formation efficiency and specific SFR derived for RXJ1131 are comparable to those of 
non-AGN host disk galaxies at $z$\ssim1$-$1.5, and that the 
derived molecular gas mass fraction is consistent with the redshift evolution reported in other studies. 
We thus find no evidence of negative AGN feedback on the molecular gas content 
and on the star formation activity in RXJ1131 at the resolution of our data.
Our results suggest that for some AGN host galaxies at intermediate redshift, 
their contribution to the decline in the cosmic star formation history since $z$\ssim2 is mainly a 
manifestation of the redshift evolution in the molecular gas content 
rather than a result of the negative feedback driven by their central AGNs.
